Missing The Point

### 2020-09-16 Manuscript.Rmd
Compute convergence diagnostics and plot results

>>>>

## Some results

```{r echo=FALSE}
load("~/MissingThePoint/Data/results.Rdata")
results %>%
  ggplot() +
  geom_hline(yintercept = 0.3334) +
  geom_point(aes(x=it, y=est, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=est, color = mech, linetype = as.factor(p))) +
  theme_classic()

```

Bias in estimate depends mostly on the amount of missingness (less info to estimate the relation??), but overall MNAR performs the worst, which is stable after it=5.

```{r}
results %>%
  ggplot() +
  geom_hline(yintercept = 0.95) +
  geom_point(aes(x=it, y=cov, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=cov, color = mech, linetype = as.factor(p))) +
  theme_classic()

```

Cov is more or less fine, except for MNAR with only 0.05% incomplete cases --> due to bias in the estimate in combination with very narrow CI (see CIW!). However, all stable after it=3??

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=CIW, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=CIW, color = mech, linetype = as.factor(p))) +
  theme_classic()

```

CIW clearly determined by the proportion of incomplete cases. Worst for p=0.95, then stable after it 7.

```{r}
results %>%
  ggplot() +
  geom_hline(yintercept = 0.2090) +
  geom_point(aes(x=it, y=rsq, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=rsq, color = mech, linetype = as.factor(p))) +
  theme_classic()

```

Magnitude of the bias in R^2 perfectly follows the missingness mechanisms: least bias for MCAR, most for MNAR. Worst effect of non-convergence for p=0.95, MNAR, but stable from it=5.

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=ac.max.lambda, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=ac.max.lambda, color = mech, linetype = as.factor(p))) +
  theme_classic()
```

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=r.hat.max.lambda, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=r.hat.max.lambda, color = mech, linetype = as.factor(p))) +
  theme_classic()

```
